Expert-In-The-Loop Causal Discovery: \\ Iterative Model Refinement Using Expert Knowledge

### 2025-02-10 paper/main.tex
Updates

To implement Algorithm~\ref{algo:ranked_expand}, we need to have an effect size 
metric by which we can rank effects. For some simple cases, such as 
linear-Gaussian models, such effect sizes exist. However, a challenge arises
when using mixed data. We here present a standardized effect size hat 
is useable for datasets containing mixtures of continuous, ordinal and

The
algorithm selects the edge that has the highest absolute residual association,
resulting in prioritization of edges that contribute the most to improving the
model.

@@

We analyzed the performance of \textsc{ExpertInLoop} algorithm by comparing it
with three other automated algorithms: PC, Hill-Climb Search, and Greedy
Equivalence Search (GES) on linear Gaussian data. For \textsc{ExpertInLoop}, we
use the \textsc{RankedExpand} method with Pearson's correlation coefficient as
the effect size measure (Section~\ref{ref:ci_tests}). For the analysis, we
simulated data from known DAGs and use the algorithms to recover the original
DAG. We start by generating a random DAG on $10$ nodes and use linear models
with random effects to simulate $ 500 $ samples from it. We simulate each
variable $ V_i $ in the DAG as:

>>>>

To implement Algorithm~\ref{algo:ranked_expand}, we need to have an effect size
metric by which we can rank effects. Depending on the type of variables, we can
use the effect size measures shown in Section~\ref{sec:ci_tests}. The algorithm
selects the edge that has the highest absolute residual association, resulting
in prioritization of edges that contribute the most to improving the model.

@@

We analyzed the performance of \textsc{ExpertInLoop} algorithm by comparing it
with three other automated algorithms: PC, Hill-Climb Search, and Greedy
Equivalence Search (GES) on linear Gaussian data. For \textsc{ExpertInLoop}, we
use the \textsc{RankedExpand} method with Pearson's correlation coefficient as
the effect size measure (Section~\ref{sec:ci_tests}). For the analysis, we
simulated data from known DAGs and use the algorithms to recover the original
DAG. We start by generating a random DAG on $10$ nodes and use linear models
with random effects to simulate $ 500 $ samples from it. We simulate each
variable $ V_i $ in the DAG as:
